Autonomous Aerial for Topological Mapping of Mars Environments

### 2018-06-09 Conference/SCITECH19/SCITECH19.tex
added resulting figs, still 3 paragraphs for results and 1-2 for conclusions

First we define the map, measurements, and poses as follows. Let 3D map $m$ be composed of $n_m$ evenly-spaced cubic grid cells with edge length $\alpha$. For index $i\in\braces{1,2,\ldots,n_m}$, let $\mathbf{m}_i$ and $\bar{\mathbf{m}}_i$ be the events that the $i$-th grid cell are occupied and free, respectively, where each cell occupancy is assumed static, binary, and independent of other cells. At the $t$-th time step, we assume a known current pose $X_t=\braces{x_t,R_t}$ such that $x_t\in\Re^3$ is a 3D location and $R_t\in\SO$ is the 3D attitude, and history of poses $X_{1:t-1}$ is assumed known as well. Considering that most modern sensors return scans with multiple measurement rays, let measurement ray $z\in\Sph^2$ belong the the most recent scan $Z_t$, and let $Z_{1:t-1}$ be the history of measurement scans.

@@

Here we describe how a reduced map is generated for collision avoidance and motion planning. If the largest edge-to-edge distance of the robot, namely $\rho$, is not larger than the 3D grid cell size $\alpha$, this step is unnecessary. Let $k\geq1$ be an integer such that $k\alpha\geq\rho$ and $(k-1)\alpha<\rho$, i.e., $k$ is the minimum number of grid cells in each dimension capable of fully-enclosing the robot inside this cube. Then, we decompose the complete probabilistic 3D into map $m_\text{reduced}$, which is composed of larger cubic cells that encompass $k^3$ cells from map $m$. Let $\mathbf{m}_{\text{reduced},k}$ denote the $k$-th cell of $m_\text{reduced}$ being occupied, and let $a_k\subset m$ be those $k^3$ cells from $m$ composing this larger cell. Then, we apply an effective rule for collision-avoidance from~\cite{KauTakAiLee18} to obtain the probability of $\mathbf{m}_{\text{reduced},k}$,

@@

Next, we show how $\mathbf{m}_{\text{reduced},k}$ is used in Dijkstra's search~\cite{Dij59}. Defining $0<P_\text{coll}<1$ as the acceptable probability of collision, every grid cell of $m_\text{reduced}$ is considered a safe and unvisited node if its occupancy probability, and the occupancy probabilities of its neighbors (sharing a face, edge, or corner), are below $P_\text{coll}$. A cost map is built from the starting robot location by neighboring nodes, where the cost to travel to another node is based on Euclidian distance: a cell sharing a face is $\alpha$ away, a cell sharing an edge is $\sqrt2\alpha$ away, and a cell sharing a corner is $\sqrt3\alpha$ away. Generating a cost map for all reachable cells in $\mathbf{m}_{\text{reduced},k}$ provides a collision-free travel cost for all reachable candidate pose locations. Once an optimal pose is selected, the path is easily found from the cost map using steepest descent.

@@

The mapping, exploration, and visualization processes communicate over the Robot Operating System (ROS) framework, and Gazebo 8 serves as the simulator for the physical objects and measurements. There are two major programs, referred to as \emph{nodes} in ROS, used during the simulation: mapping and exploration. The mapping node takes measurements from a 3D laser scanner and pairs those with the sensor transformation relative to Mars using the ROS Transform Message Filters package. Then, it builds a 3D probabilistic map using \refeqn{RayISMAnswer}-\refeqn{Unnormalized}. The mapping node sends updates from the probabilistic map to the exploration node, which decomposes the map into $m_\text{reduced}$ according to \refeqn{Proj3DMapComb}, and builds a cost map based on Dijkstra's search to determine collision-free trajectory costs for all pose candidates. Finally, it applies \refeqn{RcStar}, \refeqn{BumpFunRecedingHorizon}, and \refeqn{CandidateLocationOptimization} to update the desired robot trajectory on a receding-horizon. An overview of the process is illustrated in Fig. \ref{fig:NodesDiagram}.

@@

A 3D environment of Mars is simulated in Gazebo. A height map~\cite{mapaplanet} is used to generate a contoured surface, and the corresponding picture of Mars is draped over this contour, shown in Fig. \ref{fig:MarsGazebo}. A laser scanner was also simulated in Gazebo. In the horizontal direction, the sensor has limits $\Psi=120\degree$ with a total of $1000$ measurement rays inside, the sensor is fixed at angle $\tilde{\psi}=45\degree$, and $n_\psi=16$ sample measurements are used. In the vertical direction, the sensor also has limits $\Theta=120\degree$ with a total of $1000$ measurement rays inside, but the sensor is fixed at angle $\tilde{\theta}=30\degree$, and $n_\psi=7$ sample measurements are used. These ray samples are taken from candidate locations separated $1$m apart in each dimension.

@@

\begin{figure}[!t]
	\centering
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[height=0.9\textwidth]{mars_heightmap.png}
        		\caption{Height Map}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[height=0.9\textwidth]{mars_colormap.png}
        		\caption{Color Map}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering{
          	\includegraphics[height=0.9\textwidth]{mars_gazebo_sqr.png}}
        		\caption{Gazebo Environment}
    	\end{subfigure}
%	\begin{subfigure}[t]{0.3\columnwidth}
%           	\centering
%          	\includegraphics[trim = {23cm 4cm 17cm 6cm}, clip, height=1.0\textwidth]{mars_theta.png}
%        		\caption{$\theta$ Rotation}
%    	\end{subfigure}
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
\caption{The height map (a) and color map (b) are used in Gazebo (c) to simulate a Mars environment.}
\label{fig:MarsGazebo}
\end{figure}

The map parameters are also important to the success of the exploration. The full map has dimensions $20$m$\times20$m$\times5$m in the Mars-fixed frame, with cell edge length $\alpha=0.075$m. The reduced map for collision-avoidance and motion planning has cells $k=3$ times the size ($0.225$m), so $k^3=27$ cells are considered in \refeqn{Proj3DMapComb}. The bump functions use $f_\text{max}=1.0$, $f_\text{far}=0.1$, and $\beta=0.1$ to account for travel costs with \refeqn{BumpFunRecedingHorizon}. The receding horizon optimal time $d_\text{opt}$ is based on a fixed robot velocity of $0.5$m/sec and the computation time varies from $0.6$sec to $1.0$sec.

The simulation is run twice. Case 1 is as described in this paper. Case 2 is identical, except the reduced map $m_\text{reduced}$ is used when computing \refeqn{Iscan}. Case 2 is largely inspired by the promising results of~\cite{KauTakAiLee18}, where a projected map based on the same criteria as \refeqn{Proj3DMapComb} provided useful effective information during level flight. The resulting occupancy grid maps and complete map entropy are shown in Figs. \ref{mars3Dogm} and \ref{fig:mars3Dentropy}, respectively.

@@

\begin{itemize}
	\item Mars Environment: simulation environment generation, depth sensor facing slightly downward
	\item Full map/reduced map for entropy options
	\item Numerical Results: reduced map used for entropy, full map used for entropy, Figs: RGB/heightmap/Gazebo, 3D colored grid cells with candidates (both full and reduced maps), entropy over time (full and reduced on same plot)
\end{itemize}

>>>>

First we define the map, measurements, and poses as follows. Let 3D map $ m$ be composed of $n_m$ evenly-spaced cubic grid cells with edge length $\alpha$. For index $i\in\braces{1,2,\ldots,n_m}$, let $\mathbf{m}_i$ and $\bar{\mathbf{m}}_i$ be the events that the $i$-th grid cell are occupied and free, respectively, where each cell occupancy is assumed static, binary, and independent of other cells. At the $t$-th time step, we assume a known current pose $X_t=\braces{x_t,R_t}$ such that $x_t\in\Re^3$ is a 3D location and $R_t\in\SO$ is the 3D attitude, and history of poses $X_{1:t-1}$ is assumed known as well. Considering that most modern sensors return scans with multiple measurement rays, let measurement ray $z\in\Sph^2$ belong the the most recent scan $Z_t$, and let $Z_{1:t-1}$ be the history of measurement scans.

@@

Here we describe how a reduced map is generated for collision avoidance and motion planning. If the largest edge-to-edge distance of the robot, namely $\rho$, is not larger than the 3D grid cell size $\alpha$, this step is unnecessary. Let $k\geq1$ be an integer such that $k\alpha\geq\rho$ and $(k-1)\alpha<\rho$, i.e., $k$ is the minimum number of grid cells in each dimension capable of fully-enclosing the robot inside this cube. Then, we decompose the complete probabilistic 3D into map $ m_\text{reduced}$, which is composed of larger cubic cells that encompass $k^3$ cells from map $ m$. Let $\mathbf{m}_{\text{reduced},k}$ denote the $k$-th cell of $ m_\text{reduced}$ being occupied, and let $a_k\subset m$ be those $k^3$ cells from $ m$ composing this larger cell. Then, we apply an effective rule for collision-avoidance from~\cite{KauTakAiLee18} to obtain the probability of $\mathbf{m}_{\text{reduced},k}$,

@@

Next, we show how $\mathbf{m}_{\text{reduced},k}$ is used in Dijkstra's search~\cite{Dij59}. Defining $0<P_\text{coll}<1$ as the acceptable probability of collision, every grid cell of $ m_\text{reduced}$ is considered a safe and unvisited node if its occupancy probability, and the occupancy probabilities of its neighbors (sharing a face, edge, or corner), are below $P_\text{coll}$. A cost map is built from the starting robot location by neighboring nodes, where the cost to travel to another node is based on Euclidian distance: a cell sharing a face is $\alpha$ away, a cell sharing an edge is $\sqrt2\alpha$ away, and a cell sharing a corner is $\sqrt3\alpha$ away. Generating a cost map for all reachable cells in $\mathbf{m}_{\text{reduced},k}$ provides a collision-free travel cost for all reachable candidate pose locations. Once an optimal pose is selected, the path is easily found from the cost map using steepest descent.

@@

The mapping, exploration, and visualization processes communicate over the Robot Operating System (ROS) framework, and Gazebo 8 serves as the simulator for the physical objects and measurements. There are two major programs, referred to as \emph{nodes} in ROS, used during the simulation: mapping and exploration. The mapping node takes measurements from a 3D laser scanner and pairs those with the sensor transformation relative to Mars using the ROS Transform Message Filters package. Then, it builds a 3D probabilistic map using \refeqn{RayISMAnswer}-\refeqn{Unnormalized}. The mapping node sends updates from the probabilistic map to the exploration node, which decomposes the map into $ m_\text{reduced}$ according to \refeqn{Proj3DMapComb}, and builds a cost map based on Dijkstra's search to determine collision-free trajectory costs for all pose candidates. Finally, it applies \refeqn{RcStar}, \refeqn{BumpFunRecedingHorizon}, and \refeqn{CandidateLocationOptimization} to update the desired robot trajectory on a receding-horizon. An overview of the process is illustrated in Fig. \ref{fig:NodesDiagram}.

@@

A 3D environment of Mars is simulated in Gazebo. A height map~\cite{mapaplanet} is used to generate a contoured surface, and the corresponding picture of Mars is draped over this contour, shown in Fig. \ref{fig:MarsGazebo}. A laser scanner was also simulated in Gazebo. In the horizontal direction, the sensor has limits $\Psi=120\degree$ with a total of $1000$ measurement rays inside, the sensor is fixed at angle $\tilde{\psi}=45\degree$, and $n_\psi=16$ sample measurements are used. In the vertical direction, the sensor also has limits $\Theta=120\degree$ with a total of $1000$ measurement rays inside, but the sensor is fixed at angle $\tilde{\theta}=30\degree$, and $n_\psi=7$ sample measurements are used. These ray samples are taken from candidate locations separated $1$ m apart in each dimension.

@@

\begin{figure}[!t]
	\centering
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[height=0.9\textwidth]{mars_heightmap.png}
        		\caption{Height Map}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[height=0.9\textwidth]{mars_colormap.png}
        		\caption{Color Map}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering{
          	\includegraphics[height=0.9\textwidth]{mars_gazebo_sqr.png}}
        		\caption{Gazebo Environment}
    	\end{subfigure}
\caption{The height map (a) and color map (b) are used in Gazebo (c) to simulate a Mars environment.}
\label{fig:MarsGazebo}
\end{figure}

The map parameters are also important to the success of the exploration. The full map has dimensions $20$ m$\times20$ m$\times5$ m in the Mars-fixed frame, with cell edge length $\alpha=0.075$ m. The reduced map for collision-avoidance and motion planning has cells $k=3$ times the size ($0.225$ m), so $k^3=27$ cells are considered in \refeqn{Proj3DMapComb}. The bump functions use $f_\text{max}=1.0$, $f_\text{far}=0.1$, and $\beta=0.1$ to account for travel costs with \refeqn{BumpFunRecedingHorizon}. The receding horizon optimal time $d_\text{opt}$ is based on a fixed robot velocity of $0.5$ m/sec and the computation time varies from $0.6$ sec to $1.0$ sec.

The simulation is run twice. Case 1 is as described in this paper. Case 2 is identical, except the reduced map $ m_\text{reduced}$ is used when computing \refeqn{Iscan}. Case 2 is largely inspired by the promising results of~\cite{KauTakAiLee18}, where a projected map based on the same criteria as \refeqn{Proj3DMapComb} provided useful effective information during level flight. The resulting occupancy grid maps and complete map entropy are shown in Figs. \ref{fig:mars3Dogm} and \ref{fig:mars3Dentropy}, respectively.

\begin{figure}[!t]
	\centering
	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsFullMap1min.jpg}
        		\caption{Case 1: $1$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsRdcdMap1min.jpg}
        		\caption{Case 2: $1$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
	\centering
	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsFullMap2min.jpg}
        		\caption{Case 1: $2$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsRdcdMap2min.jpg}
        		\caption{Case 2: $2$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
	\centering
	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsFullMap5min.jpg}
        		\caption{Case 1: $5$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsRdcdMap5min.jpg}
        		\caption{Case 2: $5$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
	\centering
	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsFullMap10min.jpg}
        		\caption{Case 1: $10$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsRdcdMap10min.jpg}
        		\caption{Case 2: $10$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
	\centering
	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsFullMap15min.jpg}
        		\caption{Case 1: $15$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsFullMap20min.jpg}
        		\caption{Case 1: $20$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
\caption{The robot (red disk with arrow indicating laser direction) moves toward candidate poses (red arrows, more opaque for greater reward) while generating a 3D probabilistic occupancy grid map (cubes: greater opacity for greater occupancy probability) of the surface of Mars.}
\label{fig:mars3Dogm}
\end{figure}

	\begin{figure}
		\centerline{
			\includegraphics[width=0.6\columnwidth]{mars_H_comparison_flat.pdf}
		}
		\caption{The complete map entropy for Case 1 (red solid line) decreases at roughly the same rate as the reduced map entropy for Case 2 (dashed blue line), but the complete map entropy highlights a few locations where entropy can decrease further, shown by lower entropy over the subsequent $10$ min.}
		\label{fig:mars3Dentropy}
	\end{figure}

NEXT: ADD 3 PARAGRAPHS

@@
